\documentclass[margin, 10pt]{res}
\usepackage{helvet}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage{etaremune}
\setlength{\textwidth}{5.1in}
\begin{document}
\moveleft.5\hoffset\centerline{\large\bf Dmitry Reznitsky} 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip 
\moveleft.5\hoffset\centerline{+41788677190 reznitsky@gmail.com}
\moveleft.5\hoffset\centerline{Loretohoehe 1, 6300 Zug, Switzerland  }
\moveleft.5\hoffset\centerline{(\href{http://www.reznitsky.info}{reznitsky.info})}
\begin{resume}
\section{Profile}  
Engineering manager, software developer with more than 20 years of professional experience in building complex, multi-tiered applications in various business domains. My primary interest and focus are with scalable, high performance applications that directly influence business processes and actively contribute to company advancement. I have experienced and participated in all stages of software development cycle under different methodologies, such as, waterfall, agile, Scrum etc. Latest experience was focused on delivering mission critical portfolio management infrastructure that requires a difficult combination of high performance/throughput with robust persistence. I look for a position that offers business challenges that can be addressed with sophisticated IT solutions and strong sense of ownership. 
\section{Skills}
Object-oriented programming, application design, business and technical requirements analysis, architecture and design of complex server side solutions, distributed systems, messaging systems, development methodologies and processes, automated trading solutions, high performance/throughput servers, mentoring junior developers, conducting technical interviews, code review, source code analysis  

C\#, .NET, Java, C/C++, SQL, T-SQL, PL-SQL, Tibco Rendezvous, IBMMQ, MSMQ, Active MQ, Windows, Unix, Linux, Solaris, Git, SVN, CVS, Perforce, ANT, Maven, YouTrack, JIRA, Sourceforge  

\section{Experience}

\section{\href{http://lgtcp.com}{LGT ILS Partners}}
{\sl Engineering manager, front-office development} \hfill 2013 - Present \\
I joined LGT ILS Partners with the initial goal of extending and supporting their existing portfolio management tool, a Java/Swing application. However, as time progressed, it became clear that in order to meet future needs and address broader business requirements, a new project had to be initiated. This new project aimed to replace the existing tool, bringing it up to modern application standards, enhancing the development process, incorporating additional data sources, establishing connections with various counterparties, automating operational tasks, and introducing much-needed business intelligence capabilities. The new portfolio management tool, built with C\#, MS SQL, and React, encompasses several modules including: 
\begin{itemize}
\item Position tracking  
\item Performance calculation for different product types 
\item Risk Management 
\item Reconciliation with fund administration
\item FIX integration
\item Data consumption from various data providers (external and internal)
\item SWIFT data processing 
\item Reporting
\item BI
\end{itemize} 

 As the project progressed, my role evolved into a project lead position. In this capacity, I have assumed responsibility for a range of crucial project tasks, including long-term project planning and strategy, sprint planning for short-term objectives, requirements management, stakeholder communication, cross-functional team collaboration, release planning and roadmapping, performance review, product backlog management, liaison with company IT, support for development infrastructure (such as SCM, issue tracking, and CI/CD), and backend development involvement as a software developer. Additionally, as a member of the frontoffice development team, I am responsible for providing first-line support

\section{\href{http://imc.nl}{IMC Trading}}
{\sl Software Developer} \hfill 2008 - 2013 \\
{\sl Equity and Futures Market Making Team} \\
I joined the team almost since its inception and was closely involved in all green-field development of trading strategies and the high performance simulation engine that uses full depth order book historical data. Later, I focused on development of robust real-time monitoring tools. \\  
Technologies: Java, GWT, Hibernate, MySQL, MS SQL, Matlab  

{\sl Front office applications development for ETF desk  } \\
Implementation and support of various centralized components that facilitated the whole ETF trading desk during intraday trading. First, a centralized FX hedging component with smart rules based on internal position matching. Second, a real-time risk monitor that displays main metrics. Third, static data storage provides consistent view on market instruments and pricing for both research and trading.  \\
Technologies: Java, Swing, Hibernate, Active MQ, XML, MySQL, MS SQL  

{\sl Application development for Algorithmic Trading Group }\\
Various works on the existing trading infrastructure, such as integration of a third party market data feed into existing trading environment, cross-platform communication between trading components and integration of third party trading components (position keeping, order routing, market data feed).\\
Technologies: Java, JNI, C++, C

\section{\href{http://db.com}{Deutsche Bank}}
{\sl Software Developer} \hfill 2004 - 2008 \\
{\sl Development and support of Arina Execution System } \\
Arina is an electronic order execution system that provides Deutsche Bank traders with a standard platform that covers all markets across the globe. Server-side processes run on a  wide variety of different hardware ranging from powerful Solaris boxes to relatively small PCs working under Linux or Solaris. The system is able to support hundreds of concurrent users operating from a single location. Arina comprises components written in C++ (server), Java (server) and Java Swing(GUI), C\# (GUI), Oracle (database)

{\sl Algorithmic trading engine }\\
Working in a small team (10 people) on the implementation of the new generation algorithmic trading engine, including market data access, exchange connectivity, etc. This project was a 
basis of the smart order routing that complies with strict MiFiD regulations.  

Technologies: C++, TIBCO Rendezvous, FIX, Sun, Linux   

\section{\href{http://epicor.com}{Scala/Epicor}}
{\sl Software Developer} \hfill 2002 - 2004 \\
Design and development of the next generation ERP software (ERPII). The core systems are entirely implemented in C++ with .Net base web services for client's connectivity.\\
Technologies: C++, .Net, Web Services, XML 

\section{\href{http://softlab.ru}{R-Style Software Lab}}
{\sl Software Developer} \hfill 2000 - 2002 \\
Development and support of the core services of a major Russian based retail banking software. A classical 3-tier application framework with business and application layers. MS Windows as the main platform with support of Sun Solaris and IBM AS/400.\\
Technologies: C++, MFC, ATL 

\section{Education}
MSc in Computer Science, Moscow State Institute of Electronics and Mathematics GPA: 
4.15/5.00 


\section{Certificates}
\begin{itemize}
\item 2004 Master C++ Programmer, BrainBench  
\item 1999 Certified Unix Programmer, BrainBench  
\item 1999 Certified C Programmer, BrainBench  
\item 1999 Certified Unix Administrator, BrainBench 
\end{itemize} 

\section{Miscelenia}
{\sl Languages}
\begin{itemize}
\item English - fluent 
\item German - advanced 
\item Italian - beginner 
\item French - beginner
\item Russian - native
\end{itemize} 

{\sl Hobbies}
Photography, cycling, fly-fishing, flying (PPL), hiking.

{\sl Family}
Married with three children.

\end{resume}
\end{document}
